### 2012-01-22 docs/SDC/sdc.tex
tweaks
add graphical flowchart

\paragraph{Species Source Terms.}
For the species prediction, the form of $I_{\rho X_k}$ depends on
{\tt species\_pred\_type} (see \S \ref{sec:pred:density}):  
\begin{itemize}
\item {\tt species\_pred\_type} = 1 (predict $\rho'$ and $X_k$)
%
\begin{equation}
I_{\rho X_k} = \frac{1}{\rho^{n+\half}} \left [ 
      \frac{(\rho X_k)^\mathrm{new} - 
            (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k}  \right ]
\end{equation}

@@

\item {\tt species\_pred\_type} = 3 (predict $\rho$ and $X_k$)
%
\begin{equation}
I_{\rho X_k} = \frac{1}{\rho^{n+\half}} \left [ 
      \frac{(\rho X_k)^\mathrm{new} - 
            (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k}  \right ]
\end{equation}

@@

\paragraph{Enthalpy Source Terms.}
For the enthalpy prediction, the form of $I_{\rho h}$ depends on
{\tt enthalpy\_pred\_type} (see \S \ref{sec:pred:enthalpy}).:
\begin{itemize}
\item {\tt enthalpy\_pred\_type} = 1 \\
not right -- should be pert form
\begin{equation}
I_{\rho h}  = \frac{(\rho h)^\mathrm{new} - (\rho h)^\mathrm{old}}{\Delta t} - A_{\rho h}
\end{equation}
\end{itemize}

This is done in {\tt advance.f90} just after the call to {\tt react\_state},
stored in the \multifab\ {\tt intra}.

These terms are used as the source terms for the
advection step in the next SDC iteration.

>>>>

\paragraph{Species Source Terms.}
For the species prediction, the form of $I_{\rho X_k}$ depends on
{\tt species\_pred\_type} (see \S \ref{sec:pred:density}):  
\begin{itemize}
\item {\tt species\_pred\_type} = 1 (predict $\rho'$ and $X_k$)
%
\begin{equation}
I_{\rho X_k} = \frac{1}{\rho^{n+\myhalf}} \left [ 
      \frac{(\rho X_k)^\mathrm{new} - 
            (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k}  \right ]
\end{equation}

@@

\item {\tt species\_pred\_type} = 3 (predict $\rho$ and $X_k$)
%
\begin{equation}
I_{\rho X_k} = \frac{1}{\rho^{n+\myhalf}} \left [ 
      \frac{(\rho X_k)^\mathrm{new} - 
            (\rho X_k)^\mathrm{old}}{\Delta t} - A_{\rho X_k}  \right ]
\end{equation}

@@

\paragraph{Enthalpy Source Terms.}
For the enthalpy prediction, the form of $I_{\rho h}$ depends on
{\tt enthalpy\_pred\_type} (see \S \ref{sec:pred:enthalpy}).:
\begin{itemize}
\item {\tt enthalpy\_pred\_type} = 1 \\
not right -- should be pert form
if we do something in perturbational form, then don't we need to have
the base state see the reaction term in its prediction?
\begin{equation}
I_{\rho h}  = \frac{(\rho h)^\mathrm{new} - (\rho h)^\mathrm{old}}{\Delta t} - A_{\rho h}
\end{equation}
\end{itemize}

\ \\
This is done in {\tt advance.f90} just after the call to {\tt react\_state},
stored in the \multifab\ called {\tt intra}.
These terms are used as the source terms for the
advection step in the next SDC iteration.
